---
title: "Automatic Sampling and Analysis of YouTube Data"
subtitle: "Recap - Outlook - Practice"
author: "Julian Kohne<br />Johannes Breuer<br />M. Rohangis Mohseni"
date: "2020-02-11"
location: "GESIS, Cologne, Germany"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["default", "default-fonts", "../workshop.css"]
    nature:
      highlightStyle: "github"
      highlightLines: true
      countIncrementalSlides: false
---
layout: true

```{r setup, include = FALSE}
if (!require(easypackages)) install.packages("easypackages")
library(easypackages)

packages(
  "knitr",
  "rmarkdown",
  "tibble",
  "magrittr",
  "hadley/emo",
  prompt = FALSE
)

options(htmltools.dir.version = FALSE)

opts_chunk$set(echo = FALSE, fig.align = "center")
```

<div class="my-footer">
  <div style="float: left;"><span>`r gsub("<br />", " & ", gsub("<br /><br />|<a.+$", "", metadata$author))`</span></div>
  <div style="float: right;"><span>`r metadata$location`, `r metadata$date`</span></div>
  <div style="text-align: center;"><span>`r gsub(".+<br />", " ", metadata$title)`</span></div>
  </div>
  
---

# Course Recap (1)

```{r recap 1, echo = F}
tribble(
  ~"Session", ~"Example content", 
  "Introduction", "Why is YouTube data interesting for research?",
  "The YouTube API", "API access, API requests, quota limits",
  "Tools for the automatic sampling of YouTube data", "YouTube Data Tools (+Demo), Webometric Analyst, tuber",
  "Collecting data with the tuber package for R", "Collecting channel/video stats & viewer comments", 
  "Processing and cleaning user comments", "Character encoding, string operations, emoji dictionaries"
) %>% 
kable(
    format = "html"
  , align = "ll"
  , escape = FALSE
)
```



---

# Course Recap (2)

```{r recap 2, echo = F}
tribble(
  ~"Session", ~"Example content", 
  "Basic text analysis of user comments", "Counting and visualizing the frequencies of words and emojis in comments",
  "Sentiment analysis of user comments", "Assigning sentiment scores to words and emojis",
  "Excursus: Retrieving video subtitles", "Retrieving and parsing YouTube video subtitles (+Demo)"
) %>% 
kable(
    format = "html"
  , align = "ll"
  , escape = FALSE
)
```

---

# Where to go From Here?

Some topics that we did not cover or only briefly touched upon that you might want to explore next/further:

- Analyses for more than one video: use for-loops, functions from the `apply` family or `map` functions from the [`purrr` package](https://purrr.tidyverse.org/)

- Advanced text mining and NLP: check out the introductions/tutorials mentioned in the session on basic text analysis and/or the *GESIS* workshop ["Research Factory for Text Mining in the Social Sciences"](https://training.gesis.org/?site=pDetails&child=full&pID=0x7C279142645144CB854441D0AD613445), March 23-25, Cologne

- Topic models: have a look at the introductions/tutorials by [Julia Silge](https://juliasilge.com/blog/sherlock-holmes-stm/) and the [*Pew Research Center*](https://medium.com/pew-research-center-decoded/an-intro-to-topic-models-for-text-analysis-de5aa3e72bdb)

---

# Acknowledgements `r ji("heart")`

All slides were created with the `R` package [`xaringan`](https://github.com/yihui/xaringan) which builds on [`remark.js`](https://remarkjs.com), [`knitr`](http://yihui.name/knitr), and [`R Markdown`](https://rmarkdown.rstudio.com). The exercises were created with the [`unilur` package](https://github.com/koncina/unilur).  

The original inspiration for our emoji parsing and analyses came from a [blog post](http://opiateforthemass.es/articles/emoji-analysis/) by [Jessica Peterka-Bonetta](https://github.com/today-is-a-good-day). The `workshop.css` file we used for the layout of the slides includes elements from `CSS` files for `xaringan` presentations by [Frederik Aust](https://github.com/crsh) and [David Zimmer](https://github.com/DavZim).  

We thank Laura Rüwe and the *GESIS* Training team for taking good care of the organization of this workshop, and all of you for participating!

---

class: center, middle

# Any final questions or comments?

---

class: center, middle

# Practice time
## You now have some time to start or continue working on your own *YouTube* data analysis project. We'll be around, so feel free to ask questions. 


