---
title: 'Exercises - Preprocessing and Data Cleaning'
author: 'Julian Kohne'
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  unilur::tutorial_html_solution: default
  unilur::tutorial_pdf_solution: default
  unilur::tutorial_pdf: default
  unilur::tutorial_html: default
---

```{r knitr_init, echo=FALSE, cache=FALSE, include=FALSE}
# custom boxes
knitr::opts_template$set(clues = list(box.title = "Clues",
                                      box.body = list(fill = "#fff9dc", colour = "black"),
                                      box.header = list(fill = "#ffec8b", colour = "black"),
                                      box.icon = "fa-search",
                                      box.collapse = TRUE))

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy()
```

In these exercises, we will be going through the dataset you scraped and preprocess it for further analysis. If you couldn't scrape your own dataset for some reason, you can use one provided by us: `RawComments.Rds`. Should you run into any problems, try using the clue boxes or asking us for help. For the solutions, we will be using the prepared dataset; if you are using your scraped one, be sure to replace the names and paths in the code accordingly.

```{block, box.title = "Exercise 1", box.body = list(fill = "white"), box.icon = "fa-star"}
Load your scraped dataset or the one we prepared for you into your R-session and assign it to a dataframe called `comments`. Get an overview of the contained variables. What do the variables describe? Why do we have missing data in some of them?
```

```{block, opts.label = "clues"}
To load the data, you can use the `readRDS()` function, to get an overview of the contained variables, you can simply use `colnames()`. To find out more about what the variables mean, you can go to the YouTube data API documentation and search for the comments ouput description.

```

```{r, results = 'hide', solution = TRUE}
# Loading dataset
comments <- readRDS("../data/RawComments.rds")

# overview of columns
colnames(comments)

```

```{block, solution = TRUE}

The [YouTube API documentation](https://developers.google.com/youtube/v3/docs/comments)

```


```{block, box.title = "Exercise 2", box.body = list(fill = "white"), box.icon = "fa-star"}
We want to remove the variables `authorProfileImageUrl`, `authorChannelUrl`, `authorChannelUrl.value`,`video_id`,`canRate` and `viewerRating` and `moderationStatus`. Create a new dataframe called `Selection` containing only the remaining variables.
```

```{block, opts.label = "clues"}
You can use the `subset()` function to keep or remove a selection of variables from a dataframe. For more information, run `?subset()`

```

```{r, results = 'hide', solution = TRUE}
# selecting only the columns we need
Selection <- subset(comments,select = -c(authorProfileImageUrl,
                                         authorChannelUrl,
                                         authorChannelId.value,
                                         videoId,
                                         canRate,
                                         viewerRating,
                                         moderationStatus))
# Checking Selection
colnames(Selection)

```

```{block, box.title = "Exercise 3", box.body = list(fill = "white"), box.icon = "fa-star"}
Check the class of the variable `publishedAt` in your new dataframe. Is this class suitable for further analysis? If not, change the class to the appropriate one and compute the time difference in publishing dates between the comment in the first row and the comment in the last row.

Do the same transformation for the variable `updatedAt`

```

```{block, opts.label = "clues"}
To check the class of the `publishedAt` variable, you can use the `class()` function. To check the formatting of the comment timestamp, you can check the [YouTube API documentation](https://developers.google.com/youtube/v3/docs/comments). To transfom character strings into datetime objects in R, you can use the base function `as.POSIXct()` or the more convenient `anytime()` function from the package with the same name.

```

```{r, results = 'hide' ,solution = TRUE}
# Checking class
class(Selection$publishedAt)

# transforming to datatime object
library(anytime)
Selection$publishedAt <- anytime(Selection$publishedAt,asUTC = TRUE)
class(Selection$publishedAt)

# computing time difference in publishing time
Selection$publishedAt[1] - Selection$publishedAt[dim(Selection)[1]]

# Transforming the updatedAt variable aswell
Selection$updatedAt <- anytime(Selection$updatedAt,asUTC = TRUE)

```

```{block, box.title = "Exercise 4", box.body = list(fill = "white"), box.icon = "fa-star"}
Check the `likeCount` variable in your data, is it suitable for numeric analysis? If not, transform it to the approrpiate class and test whether your transformation worked.

```

```{block, opts.label = "clues"}
You can use the `class()` function to check the class of an R-object. To change a class, for example from character to numeric, you can use the family of "as"-functions, for example `as.numeric()`

```
```{r, solution = TRUE}
# Checking class
class(Selection$likeCount)

# Transforming class
Selection$likeCount <- as.numeric(Selection$likeCount)

# rechecking class
class(Selection$likeCount)
summary(Selection$likeCount)

```
```{block, box.title = "Exercise 5", box.body = list(fill = "white"), box.icon = "fa-star"}
Check the `textOriginal` column in your Selection dataframe. There are still hyperlinks in the column that we should remove for later text analysis steps. Extract the hyperlinks from the `textOriginal` column into a new list called `Links`. In addition, create a new variable called `LinksDel` that contains the `textOriginal` but _without_ the hyperlinks.


```

```{block, opts.label = "clues"}
The `qdabRegex` package has many prebuild functions to detect, remove and replace specific character strings. You can for example use the `rm_url()` function to extract and replace hyperlinks. You can check it's documentation with `?rm_url()` to learn how to extract and how to replace hyperlinks.

```
```{r, solution = TRUE}
# package
library(qdapRegex)

# Checking column
View(Selection$textOriginal)

# extracting hyperlinks
Links <- rm_url(Selection$textOriginal, extract = TRUE)
head(Links,10)

# removing hyperlinks
LinksDel <- rm_url(Selection$textOriginal)
head(LinksDel,10)

```

```{block, box.title = "Exercise 6", box.body = list(fill = "white"), box.icon = "fa-star"}
Check the `LinksDel` variable to see that there are still emoji contained in the column. For our later analysis, we want to do three things:

1) Create one column without hyperlinks and emoji for easier text mining
2) Create one column where emoji are replaced by a textual description for easier text mining
3) Create one column containing only the textual description of emoji

To achieve this, we first need a dictionary of emoji and their corresponding textual descriptions in a usable format.
Load the `emo` package and have a look at the contained dataframe `jis`. Copy it to a new dataframe called `EmojiList`. Afterwards, source the provided `CamelCase.R` script (in the scripts folder) to transform the textual description from regular case into CamelCase. Finally, create a new variable called `TextEmoDel` containing the text without the emoji (you can use the `ji_replace_all()` function from the `emo` package for that)

```

```{block, opts.label = "clues"}
We provide you with a function that capitalizes the first character of each word. The function is called `simpleCap()` and the scripts name is `CamelCase.R`. You can load it into your workspace using the `source()` function and specifying it's location. You can find the function in the `scripts` folder. Keep in mind that this function is only capitalizing the first letters of each word, you still need to get rid of the extra space characters. The `gsub()` function is a handy tool for this.

```
```{r, solution = TRUE}
# loading package
library(emo)

# sourcing script
source("../scripts/CamelCase.R")

# Reassigning dataframe
EmojiList <- jis

# Applying the function to all the names
CamelCaseEmojis <- lapply(jis$name, simpleCap)

# Deleting the empty spaces
CollapsedEmojis <- lapply(CamelCaseEmojis,function(x){gsub(" ", "", x, fixed = TRUE)})

# Formatting back from a list to a vector
EmojiList[,4] <- unlist(CollapsedEmojis)

# Overview of first 3 rows
EmojiList[1:10,c(1,3,4)]

# Creating text column with removed Emoji (and hyperlinks)
TextEmoDel <- ji_replace_all(LinksDel,"")

```

```{block, box.title = "Exercise 7", box.body = list(fill = "white"), box.icon = "fa-star"}
Ultimately, we want to use our `EmojiList` dataframe to replace the instances of emoji in our text with the textual description. We can do that by looping through all emoji in all texts and replacing them one at a time. There is a problem however: Some emoji are made up of multiple "shorter" emoji. If we match part of a "longer" emoji and replace it with it's text description, the rest will become unreadble. For this reason, we need to make sure that we replace the emoji **from longest to shortest**. Sort the `EmojiList` dataframe by the length of the `emoji` column from longest to shortest.

```

```{block, opts.label = "clues"}
You can count the number of characters in a vector of text using the `nchar()` function. You can reorder dataframes using the `order` function and you can reverse an order using the `rev()` function.

```
```{r, solution = TRUE}
# ordering from longest to shortest
EmojiList <- EmojiList[rev(order(nchar(jis$emoji))),]

# Overview of new order
head(EmojiList[,c(1,3,4)],5)

```


```{block, box.title = "Exercise 8", box.body = list(fill = "white"), box.icon = "fa-star"}
We now have a working dictionary for replacing emoji with a textual description! Create a new variable called `TextEmoRep` as a copy of the `LinksDel` variable. Next, loop through the ordered `EmojiList` and for every element in `TextEmoRep`, replace the contained emoji with "EMOJI_" followed by their textual description. You can use the `rm_default()` function from the `qdapRegex` package to replace custom patterns. Be sure to check the documentation so you can set the appropriate options for the function.

Beware: There will be warnings in your console even if you are doing everything right.

```

```{block, opts.label = "clues"}
Loop through the dictionary sorted from longest to shortest emoji. You need to use a `for` loop to go through all emoji for all comments, one at a time. The `paste()` function is useful for adding the prefix "EMOJI_" in front of your textual descriptions. Don't forget to set the arguments `fixed = TRUE`, `clean = TRUE` and `trim = FALSE` in your call to `rm_default()`  

```
```{r, solution = TRUE, warning=FALSE,message=FALSE}

# Assigning the column to a new variable
TextEmoRep <- LinksDel

# switching off warnings
options(warn=-1)

# Looping through all Emojis for all comments in New
for (i in 1:dim(EmojiList)[1]) {

  TextEmoRep <- rm_default(TextEmoRep,
                    pattern = EmojiList[i,3],
                    replacement = paste0("EMOJI_",
                                       EmojiList[i,4],
                                       " "),
                    fixed = TRUE,
                    clean = FALSE,
                    trim = FALSE)
}

# checking results
LinksDel[159:171]
TextEmoRep[159:171]

```

```{block, box.title = "Exercise 9", box.body = list(fill = "white"), box.icon = "fa-star"}
We now have the original text column, and the text column with removed hyperlinks and were emoji are replaced with their textual descriptions (`TextEmoRep`). We need one more variable that _only_ contains the textual desciptions of the emoji. You can use our predefined function `ExtractEmoji()` from the scripts folder to create this variable.

```

```{block, opts.label = "clues"}
Use the `source()` function to source the `ExtractEmoji.R` script from the `scripts` folder and then `sapply()` the `ExtractEmoji()` function to the variable `TextEmoRep`. To remove useless rownames from the extracted Emojis, you can set `names(Emoji)` to `NULL`

```
```{r, solution = TRUE}
# sourcing function
source("../scripts/ExtractEmoji.R")

# Using function
Emoji <- sapply(TextEmoRep,ExtractEmoji)
names(Emoji) <- NULL

# checking results
TextEmoRep[39]
Emoji[39]

```

```{block, box.title = "Exercise 10", box.body = list(fill = "white"), box.icon = "fa-star"}
We now have selected all the variables we need, formatted them into the right formats, cleaned the text and extracted some additional information from it. Create a new dataframe called `df` that contains the following variables:

- Selection$authorDisplayName

- Selection$textOriginal

- TextEmoRep

- TextEmoDel

- Emoji

- Selection$likeCount

- Links

- Selection$publishedAt

- Selection$updatedAt

- Selection$parentId

- Selection$id

Set the following names for the column in the new dataframe:

- Author

- Text

- TextEmojiReplaced

- TextEmojiDeleted

- Emoji

- LikeCount

- URL

- Published

- Updated

- ParentId

- CommentID

Save the new dataframe as an RDS object with the name "ParsedComments.Rds"

```

```{block, opts.label = "clues"}
You can use the `cbind.data.frame()` function to paste together multiple columns to a dataframe. You need to set the argument `stringsAsFactors = FALSE` though, to prevent strings from being interpreted as factor variables. In addition, the variables `Links` and `Emoji` are lists and can contain multiple values per row. For this reason, we need to enclose them with the `I()` function to be able to put them into a dataframe. You can save your result using the `saveRDS()` function.


```
```{r, solution = TRUE}
# creating df dataframe (use I() function to enclose Emoji and Links)
df <- cbind.data.frame(Selection$authorDisplayName,
                       Selection$textOriginal,
                       TextEmoRep,
                       TextEmoDel,
                       I(Emoji),
                       Selection$likeCount,
                       I(Links),
                       Selection$publishedAt,
                       Selection$updatedAt,
                       Selection$parentId,
                       Selection$id,
                       stringsAsFactors = FALSE)

# setting column names
names(df) <- c("Author",
               "Text",
               "TextEmojiReplaced",
               "TextEmojiDeleted",
               "Emoji",
               "LikeCount",
               "URL",
               "Published",
               "Updated",
               "ParentId",
               "CommentID")

# deleting row names
row.names(df) <- NULL

# saving dataframe
saveRDS(df, file = "../data/ParsedComments.rds")

```

